Revisiting the Classics: Online RL in the Programmable Dataplane

### 2021-06-04 ngni-talk/talk.tex
Branding (tm)

	How should we adjust the value of selected items?
	$$
			\delta_t = \overbrace{R_{t+1} + \gamma \acval{S_{t+1}}{A_{t+1}}{\wvec{t}}}^{\mathclap{\substack{\text{New target value:}\\ \text{Reward} + \text{some of the next action's value}}}} - \underbrace{\acval{S_t}{A_t}{\wvec{t}}}_{\mathclap{\text{Current value estimate}}},
	$$\pause

	Policy parameter update:
	$$
			\bm{w}_{t+1} = \bm{w}_{t} + \overbrace{\alpha \delta_t}^{\mathclap{\text{Move a little bit of } \delta_t \text{ along...}}} \underbrace{\nabla{\acval{S_t}{A_t}{\wvec{t}}}}_{\mathclap{\text{...the policy's gradient}}}.
	$$\pause

	Design implications?
\end{frame}

@@

\begin{frame}{Designs: How to exploit on-NIC parallelism?}
	\begin{itemize}[<+->]
		\item Netronome SmartNICs \emph{very} multi-core.
		\begin{itemize}[<+->]
			\item NetFPGAs also allow creating separate, effectively async functional units.
		\end{itemize}
		\item Two ways to take advantage:
		\begin{itemize}[<+->]
			\item Available threads process \Indfw{}ependently.
			\item Available threads \Coopfw{}erate on each inference or learning task.
		\end{itemize}
		\item Basic algorithm:
		\begin{itemize}[<+->]
			\item (Parallel) action compute.
			\item Output action.
			\item Check for trace in progress for this input.
			\item If found: compute $\delta$, do (parallel) policy update.
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Designs: \emph{Ind}}
	\centering
	\includegraphics[width=0.52\linewidth]{../paper/figures/ind}
\end{frame}

\begin{frame}{Designs: \emph{CoOp}}
	\centering
	\includegraphics[width=0.535\linewidth]{../paper/figures/coop}
\end{frame}

@@

\begin{frame}{Metrics of interest}
	Versus commodity hosts...
	\begin{itemize}[<+->]
		\item State-Action/Update latency
		\item Online/Offline throughput
		\item Impact on cross-traffic
		\item Device resource use
	\end{itemize}
\end{frame}

@@

\begin{frame}[standout]
	Takeaways:
	\begin{itemize}
		\item \alert{Online in-NIC RL is possible!}
		\item \alert{Order-of-magnitude latency improvement} over offloading, higher online throughput.
		\item Platform-specific, but similar design for SmartNIC hardware class.
		\item \alert{Future work}: accuracy, use-cases (AQM, DDoS prevention), NetFPGA, transfer learning.
	\end{itemize}
	\alert{Questions?}\\
	{
		\scriptsize
		\vspace{2em}\faEnvelopeO{} \href{mailto:k.simpson.1@research.gla.ac.uk}{\nolinkurl{k.simpson.1@research.gla.ac.uk}}\\
		\vspace{-0.8em}	\small{\faGithub{} \href{https://github.com/felixmcfelix}{FelixMcFelix} \hspace{0.5em} \faGlobe{} \url{https://mcfelix.me}}
	}
\end{frame}

@@

>>>>

	How to select an action? Pick largest from list: $\acval{S_t}{\cdot}{\wvec{t}}$\pause

	How should we adjust the value of selected items?
	$$
			\delta_t = \overbrace{R_{t+1} + \gamma \acval{S_{t+1}}{A_{t+1}}{\wvec{t}}}^{\mathclap{\substack{\text{New target value:}\\ \text{Reward} + \text{some of the next action's value}}}} - \underbrace{\acval{S_t}{A_t}{\wvec{t}}}_{\mathclap{\text{Current value estimate}}},
	$$\pause
	Policy parameter update:
	$$
			\bm{w}_{t+1} = \bm{w}_{t} + \overbrace{\alpha \delta_t}^{\mathclap{\text{Move a little bit of } \delta_t \text{ along...}}} \underbrace{\nabla{\acval{S_t}{A_t}{\wvec{t}}}}_{\mathclap{\text{...the policy's gradient}}}.
	$$\pause
	Design implications?
\end{frame}

@@

\begin{frame}{Designs: How to exploit on-NIC parallelism?}
	\begin{itemize}[<+->]
		\item Netronome SmartNICs \emph{very} multi-core (NFP-6480).
		\begin{itemize}[<+->]
			\item NetFPGAs also allow creating separate, effectively async functional units.
		\end{itemize}
		\item Two ways to take advantage:
		\begin{itemize}[<+->]
			\item Available threads process \Indfw{}ependently.
			\item Available threads \Coopfw{}erate on each inference or learning task.
		\end{itemize}
		\item Basic algorithm:
		\begin{itemize}[<+->]
			\item (Parallel) action compute.
			\item Output action.
			\item Check for trace in progress for this input.
			\item If found: compute $\delta$, do (parallel) policy update.
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Designs: \emph{Ind} (on NFP)}
	\centering
	\includegraphics[width=0.52\linewidth]{../paper/figures/ind}
\end{frame}

\begin{frame}{Designs: \emph{CoOp} (on NFP)}
	\centering
	\includegraphics[width=0.535\linewidth]{../paper/figures/coop}
\end{frame}

@@

\begin{frame}{Metrics of interest}
	Versus commodity hosts...
	\begin{itemize}[<+->]
		\item State-Action/Update latency
		\item Online/Offline throughput
		\item Impact on cross-traffic
		\item Device resource use
	\end{itemize}\pause
	\textbf{On large-ish policies} (20D state, 10 actions, bias+(7$\times$1D, 8$\times$2D, 1$\times$4D)).
\end{frame}

@@

\begin{frame}[standout]
	Takeaways:
	\begin{itemize}
		\item \alert{Online in-NIC RL is possible!}
		\item \alert{Order-of-magnitude latency improvement} over offloading, higher online throughput.
		\item Platform-specific, but similar design for SmartNIC hardware class.
		\item \alert{Future work}: use-cases (AQM, DDoS prevention \& accuracy), NetFPGA, transfer learning.
	\end{itemize}
	\alert{Questions?}\\
	{
		\scriptsize
		\vspace{2em}\faEnvelopeO{} \href{mailto:k.simpson.1@research.gla.ac.uk}{\nolinkurl{k.simpson.1@research.gla.ac.uk}}\\
		\vspace{-0.8em}	\small{\faGithub{} \href{https://github.com/felixmcfelix}{FelixMcFelix} \hspace{0.5em} \faGlobe{} \url{https://mcfelix.me}}
	}

	\begin{tikzpicture}[overlay, remember picture]
		%		\node[above right=0.8cm and 0.9cm of current page.south west] (esnet-logo) {\includegraphics[width=2.75cm]{netlab-trim}};
		%		\node[right=1cm of esnet-logo] {\adjincludegraphics[height=2cm,trim={0 {.4\height} 0 {.05\height}},clip]{uofg}};
		\node[above left=0.2cm and 0.8cm of current page.south east] {\includegraphics[width=2.75cm]{netlab-fulllogo}};
		\node[above right=0.35cm and 0.8cm of current page.south west] {\includegraphics[width=2.75cm]{uofg-white}};
	\end{tikzpicture}
\end{frame}

@@

\begin{frame}{Latency---All \approachshort}
	\centering
	\resizebox{\linewidth}{!}{\expandableinput ../tables/build/latency}
\end{frame}

\begin{frame}{Throughput---All \approachshort}
	\centering
	\resizebox{\linewidth}{!}{\expandableinput ../tables/build/tput}
\end{frame}
